### 2016-04-04 Manuscript/Table_LaTeX/Table_results_BW.tex
Fixing BW table legend

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 22:09:15 2016
\begin{longtable}{lL{1.8cm}C{2cm}lcc}
\caption{Number of taxa with available discrete morphological data for mammalian orders at three taxonomic levels. The left vertical bar represents low coverage (\textless 25\%; coloured in blue); the right vertical bar represents high coverage (\textgreater 75\%; coloured in orange). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.
} \\

>>>>

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 22:09:15 2016
\begin{longtable}{lL{1.8cm}C{2cm}lcc}
\caption{Number of taxa with available discrete morphological data for mammalian orders at three taxonomic levels. The left vertical bar represents low coverage (\textless 25\%; coloured in dark grey); the right vertical bar represents high coverage (\textgreater 75\%; coloured in light grey). Negative Net Relatedness Index (NRI) and Nearest Taxon Index (NTI) values indicate phylogenetic overdispersion; positive values indicate phylogenetic clustering. Significant NRI or NTI values are in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.
} \\
